Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-14 Ch1_movement_rates/Ch1_Figures.Rmd
comment out saving
making table of movement rates

ggsave2(filename = "Ch1_movement_rates/Figures/Figure1.png")
```

@@

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  geom_point(size = 3, alpha = 0.8) +
  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = my.cols1[4], alpha = 0.8, size = 1) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Average movement rates lognormal fits") +
  theme_bw()
```

>>>>

# ggsave2(filename = "Ch1_movement_rates/Figures/Figure1.png")
```

@@

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  geom_point(size = 3, alpha = 0.8) +
  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
  #               color = my.cols1[4], alpha = 0.8, size = 1) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
  labs(x = "Movement Rate (meters/minute)",
       # title = "Average movement rates lognormal fits",
       y = "Density") +
  theme_bw()
```
